Project

### 2022-04-03 Project/DraftR.Rmd
Update DraftR.Rmd

---
title: "Project"
author: "Group5"
date: '2022-03-22'
output: pdf_document
---

@@

```{r}
ggplot(clim.win, aes(x = year, y = d.snowpack, color = ID)) +
  geom_point(size = 0.8, alpha = 0.8) +
  geom_line(aes(group = ID), color = "grey", size = 0.3, alpha = 0.5) +
  xlab("Winter 2010 - 2014") +
  ylab("Days with Snowpack") +
  theme_classic()
```

Figure 1.

@@

```{r}
ggplot(clim.not.win, aes(x = year, y = avmaxminTJuly, color = ID)) +
  geom_point(size = 0.8, alpha = 0.8) +
  geom_line(aes(group = ID), color = "grey", size = 0.3, alpha = 0.5) +
  xlab("Year 2011 - 2013") +
  ylab("Mean July temperature (ºC)") +
  theme_classic()
```

@@

# Mid Elevation Source Plot
# Create Mid Elevation plot
MidLeafPlot <- ggplot(MidPlotDat, aes(x = site, y = Ln.tot, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(name = "Total leaf nodes \n")+
  scale_fill_discrete(name = "Treatment", labels = c("Warmed", "Control")) +
  ggtitle("Leaf growth of mid-elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 7),
        plot.title = element_text(hjust = 0.5))

@@

# High Elevation Source Plot
# Create Mid Elevation plot
HighLeafPlot <- ggplot(HighPlotDat, aes(x = site, y = Ln.tot, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(name = "Total leaf nodes \n")+
  scale_fill_discrete(name = "Treatment", 
                      labels = c("Warmed", "Control")) +
  ggtitle("Leaf growth of high elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 7),
        plot.title = element_text(hjust = 0.5))

@@

# Mid Elevation Source Plot
# Create Mid Elevation plot
MidFruitPlot <- ggplot(MidPlotDat, aes(x = site, y = Fr.tot, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(name = "Total fruits from all stems \n")+
  scale_fill_discrete(name = "Treatment", labels = c("Warmed", "Control")) +
  ggtitle("Fruit development of mid-elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 7),
        plot.title = element_text(hjust = 0.5))

@@

# High Elevation Source Plot
# Create Mid Elevation plot
HighFruitPlot <- ggplot(HighPlotDat, aes(x = site, y = Fr.tot, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(name = "Total fruits from all stems \n")+
  scale_fill_discrete(name = "Treatment", 
                      labels = c("Warmed", "Control")) +
  ggtitle("Fruit development of high elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 7),
        plot.title = element_text(hjust = 0.5))

@@

# Mid Elevation Source Plot
# Create Mid Elevation plot
MidSeedPlot <- ggplot(MidPlotDat, aes(x = site, y = propgoodseed, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(labels = scales::percent, 
                     name = "Percentage of viable seeds produced by plant \n")+
  scale_fill_discrete(name = "Treatment", labels = c("Warmed", "Control")) +
  ggtitle("Seed viability of mid-elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 7),
        plot.title = element_text(hjust = 0.5))

@@

# High Elevation Source Plot
# Create Mid Elevation plot
HighSeedPlot <- ggplot(HighPlotDat, aes(x = site, y = propgoodseed, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(labels = scales::percent,
                     name = "Percentage of viable seeds produced by plant \n")+
  scale_fill_discrete(name = "Treatment", 
                      labels = c("Warmed", "Control")) +
  ggtitle("Seed viability of high elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 7),
        plot.title = element_text(hjust = 0.5))

>>>>

---
title: "Project"
author: "Alyssa Reynolds, Zhijun Li, Runzi Qi"
date: '2022-03-22'
output: pdf_document
---

@@

```{r}
ggplot(clim.win, aes(x = year, y = d.snowpack, color = ID)) +
  geom_point(size = 0.8, alpha = 0.8) +
  geom_line(aes(group = ID), color = "grey", size = 0.3, alpha = 0.5) +
  xlab("Winter 2010 - 2014") +
  ylab("Days with Snowpack") +
  theme_classic()
```
Figure 1. Comparison of the total days with snowpack in winter among sites sampled from elevational transect NK and HB. Grey solid lines indicate the change in days across years.

@@

```{r}
ggplot(clim.not.win, aes(x = year, y = avmaxminTJuly, color = ID)) +
  geom_point(size = 0.8, alpha = 0.8) +
  geom_line(aes(group = ID), color = "grey", size = 0.3, alpha = 0.5) +
  xlab("Year 2011 - 2013") +
  ylab("Mean July temperature (ºC)") +
  theme_classic()
```
Figure 2. Comparison of the mean July temperature (°C) among sites sampled from elevational transect NK and HB. Grey solid lines indicate the change across years from 2011 to 2013.

@@

# Mid Elevation Source Plot
# Create Mid Elevation plot
MidLeafPlot <- ggplot(MidPlotDat, aes(x = site, y = Ln.tot, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(name = "Total leaf nodes \n")+
  scale_fill_discrete(name = "Treatment", labels = c("Warmed", "Control")) +
  ggtitle("Leaf growth of mid-elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 5),
        plot.title = element_text(hjust = 0.5))

@@

# High Elevation Source Plot
# Create Mid Elevation plot
HighLeafPlot <- ggplot(HighPlotDat, aes(x = site, y = Ln.tot, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(name = "Total leaf nodes \n")+
  scale_fill_discrete(name = "Treatment", 
                      labels = c("Warmed", "Control")) +
  ggtitle("Leaf growth of high elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 5),
        plot.title = element_text(hjust = 0.5))

@@

# Mid Elevation Source Plot
# Create Mid Elevation plot
MidFruitPlot <- ggplot(MidPlotDat, aes(x = site, y = Fr.tot, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(name = "Total fruits from all stems \n")+
  scale_fill_discrete(name = "Treatment", labels = c("Warmed", "Control")) +
  ggtitle("Fruit development of mid-elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 5),
        plot.title = element_text(hjust = 0.5))

@@

# High Elevation Source Plot
# Create Mid Elevation plot
HighFruitPlot <- ggplot(HighPlotDat, aes(x = site, y = Fr.tot, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(name = "Total fruits from all stems \n")+
  scale_fill_discrete(name = "Treatment", 
                      labels = c("Warmed", "Control")) +
  ggtitle("Fruit development of high elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 5),
        plot.title = element_text(hjust = 0.5))

@@

# Mid Elevation Source Plot
# Create Mid Elevation plot
MidSeedPlot <- ggplot(MidPlotDat, aes(x = site, y = propgoodseed, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(labels = scales::percent, 
                     name = "Percentage of viable seeds produced by plant \n")+
  scale_fill_discrete(name = "Treatment", labels = c("Warmed", "Control")) +
  ggtitle("Seed viability of mid-elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 5),
        plot.title = element_text(hjust = 0.5))

@@

# High Elevation Source Plot
# Create Mid Elevation plot
HighSeedPlot <- ggplot(HighPlotDat, aes(x = site, y = propgoodseed, fill = treat)) +
  geom_boxplot(width = 0.5) +
  scale_x_discrete(name = "\n Transplant site", 
                   labels = c("Low elevation", "Mid-elevation", "High elevation", 
                              "High elevation range edge", "Above range HB",
                              "First site above range NK", "Second site above range NK")) +
  scale_y_continuous(labels = scales::percent,
                     name = "Percentage of viable seeds produced by plant \n")+
  scale_fill_discrete(name = "Treatment", 
                      labels = c("Warmed", "Control")) +
  ggtitle("Seed viability of high elevation sourced plants") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 5),
        plot.title = element_text(hjust = 0.5))
